LAGOS lake depth

### 2019-10-09 lagos_depth.Rmd
produce rayshader panels

plot_grid(
ggplot(data = hypso_ct) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = id)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("CT", " (", length(unique(hypso_ct$id)), ") lakes")) + 
  theme(legend.position = "bottom"), 
ggplot(data = hypso_mn) +
    geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") +
  ggtitle(paste0("MN", " (", length(unique(hypso_mn$llid)), ") lakes")) +
  theme(axis.title.y = element_blank()), 
rel_widths = c(1, 0.7))

@@

cowplot::plot_grid( 
ggplot(data = as.data.frame(rsub1, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("concave") +
  theme_void(),
ggplot(data = as.data.frame(rsub2, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("convex") +
  theme_void()
)
```

```{r get-hypso, eval=TRUE, fig.height = 4}
get_hypso <- function(rsub, id){
  maxdepth <- abs(cellStats(rsub, "max"))

@@

```{r eval=TRUE, fig.height = 4}
cowplot::plot_grid(
  ggplot(data = hypso, aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + 
    ylim(c(100, 0)) +  theme(legend.position = "none"),
ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0)),
rel_widths = c(0.6, 1)
)

@@

>>>>

plot_grid(
ggplot(data = hypso_ct) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = id)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("CT", " (", length(unique(hypso_ct$id)), ") lakes")) + 
  theme(legend.position = "bottom"), 
ggplot(data = hypso_mn) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") +
  ggtitle(paste0("MN", " (", length(unique(hypso_mn$llid)), ") lakes")) +
  theme(axis.title.y = element_blank(), 
        legend.position = "none"), 
rel_widths = c(1, 0.7))

@@

# gg_raster <- cowplot::plot_grid( 
gg_convave_raster <- ggplot(data = as.data.frame(rsub1, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("concave") +
  theme_void()

gg_convex_raster <- ggplot(data = as.data.frame(rsub2, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("convex") +
  theme_void()
```

```{r gg_rayshader, eval=TRUE}
library(rayshader)
library(elevatr)

tex <- create_texture("#AFEEEE", "#B0C4DE", "#B0E2FF", "#B2DFEE", "#BCD2EE")

rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")

if(!(file.exists("data/elevatr/pickerel_lake.gri") & 
     file.exists("data/elevatr/long_pond.gri"))){
  elev <- get_elev_raster(rsub1, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", names(rsub1)))

  elev <- get_elev_raster(rsub2, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", names(rsub2)))
}
elev1 <- raster::raster("data/elevatr/pickerel_lake.gri")
elev2 <- raster::raster("data/elevatr/long_pond.gri")

prep_rayshader <- function(rsub, elev){
  rsub <- rsub * -1
  maxdepth <- abs(cellStats(rsub, "min"))

  test <- crop(elev, rsub)
  test <- test - abs(cellStats(test, "min")) # test should have a min of 0
  rsub <- rsub + abs(cellStats(rsub, "max")) # rsub should have a max of 0

  test  <- mask(test, test <= (cellStats(test, "min") + 1), maskvalue = TRUE)
  test  <- resample(test, rsub)
  test2 <- merge(rsub, test)
  # test2[is.na(test2)] <- 0

  rmat                <- matrix(test2 + maxdepth, 
                                nrow = ncol(rsub), ncol = nrow(rsub))
  rmat[rmat > maxdepth] <- NA
  list(rmat = rmat, maxdepth = maxdepth, r = test2)
}
```

```{r gg-rayshader-concave, eval=TRUE}

res_rsub1 <- prep_rayshader(rsub1, elev1)
# plot(res_rsub1$r)

sphere_shade(res_rsub1$rmat, texture = tex) %>%
  plot_3d(res_rsub1$rmat, water = TRUE, waterdepth = res_rsub1$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/concave-rayshader.png", clear = TRUE)

cowplot::plot_grid(
  gg_concave_raster, 
  ggdraw() +
  draw_image("figures/concave-rayshader.png")
)
```

```{r gg-rayshader-convex, eval=TRUE}
res_rsub2 <- prep_rayshader(rsub2, elev2)

sphere_shade(res_rsub2$rmat, texture = tex) %>%
  plot_3d(res_rsub2$rmat, water = TRUE, waterdepth = res_rsub2$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/convex-rayshader.png", clear = TRUE)

cowplot::plot_grid(
  gg_convex_raster, 
  ggdraw() +
  draw_image("figures/convex-rayshader.png")
)
```

```{r get-hypso, eval=TRUE, fig.height = 4}
rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")
names(rsub1) <- "layer"
names(rsub2) <- "layer"

get_hypso <- function(rsub, id){
  maxdepth <- abs(cellStats(rsub, "max"))

@@

```{r get-hypso-normalized, eval=TRUE, fig.height = 4}
cowplot::plot_grid(
  ggplot(data = hypso, aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + 
    ylim(c(100, 0)) +  theme(legend.position = "none"),
ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0)),
rel_widths = c(0.6, 1)
)

@@

```{r }
